% ABSTRACT--------------------------------------------------------------------------------

\begin{resumo}[ABSTRACT]
\begin{SingleSpacing}

% Não altere esta seção do texto--------------------------------------------------------
\imprimirautorcitacao. \imprimirtitleabstract. \imprimirdata. \pageref {LastPage} f. \imprimirprojeto\ – \imprimirprograma, \imprimirinstituicao. \imprimirlocal, \imprimirdata.\\
%---------------------------------------------------------------------------------------

Producing quality software is one of the biggest challenges in systems development today. Testing activity in systems development is one of the most important activities that requires planning, development, execution and maintenance. The test guarantees the reduction of defects playing a fundamental role in the quality of the software. This work consists of the development of functional tests for the Integrated Pest and Disease Management (IPM) system, increasing the quality of the software, reducing the number of failures. Focus is the unit tests and components, these tests will cover all the essential functionalities of the system. Testing will provide better, stable, and easy-to-maintain software. The software testing process applied to the MIP system allowed a system aligned with the expectations of the people involved, well functioning and subject to complex verifications.



\textbf{Keywords}: Software testing. Functional Testing. Unitary tests. Integration tests. Validation. Verification.
\end{SingleSpacing}
\end{resumo}

% OBSERVAÇÕES---------------------------------------------------------------------------
% Altere o texto inserindo o Abstract do seu trabalho.
% Escolha de 3 a 5 palavras ou termos que descrevam bem o seu trabalho 
